---
title: "Anatomy of the `methyvimData` package"
author: "Nima Hejazi"
date: "`r Sys.Date()`"
output:
  BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{Anatomy of the `methyvimData` package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

This package is designed to accompany the `methyvim` analysis package by
providing example data for use with the statistical routines made available in
that package. Generally speaking, this package will likely be useless to you
without the `methyvim` package. Please consider consulting the vignettes that
accompany `methyvim`.

---

## Data

```{r deps, echo=FALSE}
suppressMessages(library(SummarizedExperiment))
suppressMessages(library(minfi))
```

This package contains a single data set. The data object is of class
`GenomicRatioSet`, an extension of the `SummarizedExperiment` container class
provided by the package `minfi`.

We can load and view the data set like so

```{r load-data}
library(methyvimData)
data(grsExample)
grsExample
```

